Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-07-24 cosmic_voids.tex
References and part of the introduction

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified as one of the most striking features 
of the Megaparsec universe, being a complementary aspect along with the 
filamentary and hierarchically clustered nature of the cosmic web 
\citep{Bond96}.

@@

Quantifying the shape of voids is gaining importance due to cosmological 
tests such as the Alcock-Paczynski test \SRKED{[Sutter, et.al (2012)]}, so 
we compute here the reduced inertia tensor through the next expression in 
order to determine shape distributions of bulk voids.

@@

%.........................................................................
%Table of sizes of each sample defined in Bolshoi
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r  r r} \hline\hline
	\textbf{Volume}					&				&\textbf{Scheme}& \\
	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\rho_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as an optimal tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified, along with the filamentary and 
hierarchically clustered nature of the cosmic web, as one of the most 
striking features of the Megaparsec universe \citep{Bond96}. Nevertheless, 
due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
Sutter12b, Nadathur14} only have become available after modern large galaxy 
surveys like the two-degree field Galaxy Survey \citep{Colless01, 
Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
thereby triggering a plethora of more refined observational and 
statistical studies of voids throughout the last decade \citep{Hoyle04,
Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}

Theoretical 
efforts for describing the evolution of the large-scale universe, leaded 
by the seminal work of \citet{Zeldovich70}, are highly consistent with the 
cosmic web picture, where planar pancake-like regions of matter enclose 
enormous sub-dense voids and are bordered, in turn, by thin filaments and
high-density clumpy knots.

@@

Quantifying the shape of voids is gaining importance due to cosmological 
tests such as the Alcock-Paczynski test \SRKED{[Sutter et al 2012]}, so 
we compute here the reduced inertia tensor through the next expression in 
order to determine shape distributions of bulk voids.

@@

%.........................................................................
%Table of sizes of each sample defined in Bolshoi
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r  r r} \hline\hline
	\textbf{volume}					&				&\textbf{scheme}& \\
	\textbf{fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}
